getdata4.Rmd

### 2022-02-24 getdata.Rmd
final commit

lagg <- 0 / 365 ##3 / 365  ## NOTE!!
tempvars <-  c("heat", "heat.1", "extemp", "extemp.1", "cold", "cold.1", "emintemp", "emeantemp", "emaxtemp", 
               "week", "year") 
## Ume:
bume <- per[per$subreg == "ume", ]
bume <- make.communal(bume, umetemp[, tempvars], 
                      start = temp_start, period = 1/52, lag = lagg)

>>>>

lagg <- 0 / 365 ##3 / 365  ## NOTE!!
tempvars <-  c("heat", "heat.1", "extemp", "extemp.1", "cold", "cold.1", "emintemp", "emeantemp", "emeantemp.1",  "emaxtemp", 
               "week", "year") 
## Ume:
bume <- per[per$subreg == "ume", ]
bume <- make.communal(bume, umetemp[, tempvars], 
                      start = temp_start, period = 1/52, lag = lagg)
